---
title: "hw24"
author: "Tin, Jade"
date: "4/20/2018"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
#install.packages("rstanarm")
```


$\textbf{3.2}$


```{r include=FALSE}
library(rstanarm)
library(ggplot2)
library(arm)
library(dplyr)
#install.packages("R2WinBUGS")
#install.packages("rstanarm")
```



```{r}
#cd4 <- read.csv("http://www.stat.columbia.edu/~gelman/arm/examples/cd4/allvar.csv")
cd4 <- read.csv("~/Desktop/allvar.csv")
cd4$sqrtCD4 <- sqrt(cd4$CD4PCT)       
cd4$time <- cd4$visage - cd4$baseage
cd4<- cd4[-which(is.na(cd4$time)),]
cd4<- cd4[-which(is.na(cd4$CD4PCT)),]
```


We need the previous exercise to complete $\textbf{(3.4)}$


$\textbf{3.3 (a)}$

```{r include=FALSE}
fit2 <- stan_glmer(sqrtCD4 ~ time + treatmnt + baseage + (1 | newpid),  data = cd4)
```
Use the model fit from Exercise 3.2(b) to generate simulation of predicted CD4 percentages for each child in the dataset at a hypothetical time point. 
```{r}
#Removing all rows with NAs because posterior_predict doesn't allow for NAs
pred_data_= cd4[complete.cases(cd4), ]

#Selecting a hypothetical time point
pred_data_$VDATE <- as.Date("1999-04-29")
#Estimating the predicted CD4 percentage for each child
newpred <- posterior_predict(fit2, newdata = pred_data_)

```

$\textbf{3.3 (b)}$
Use the same model fit to generate simulations of CD4 percentages at each of the time periods for a new child who was 4 years old at baseline. 

```{r}
#subsetting original cd4 for only when baseage is close to 4 (there is no observation where age is exactly 4)
pred_data_4yr <- subset(cd4, (baseage  > 3.99 & baseage < 4.01)) 

#removing NAs
pred_data_4yr= pred_data_4yr[complete.cases(pred_data_4yr), ]

#indicating new child with new newpid
pred_data_4yr$newpid = 300

#feed into model
pred_4yr <- posterior_predict(fit2, newdata = pred_data_4yr)


```


On to exercise $\textbf{3.4}$

FIRST VERSION:
```{r}
cd4$VDATE <- as.Date(cd4$VDATE, format = "%m/%d/%Y")
# Make the data similar to the model in mod2
finaltime_data <- subset(cd4, !is.na(treatmnt) & !is.na(baseage))
finaltime_data <- finaltime_data[complete.cases(finaltime_data), ]
# Assign the final date to the date variable
finaltime_data$VDATE <- as.Date(max(finaltime_data$VDATE, na.rm = T))

# Only select the variables present in the model
finaltime_data <- finaltime_data[, -c(1, 4, 5, 6, 8)]

# Calculate the mean predicted CD4 percentage and it's standard deviation
mean_cd4 <- mean(posterior_predict(fit2, newdata = finaltime_data), na.rm = T)
sd_cd4 <- sd(posterior_predict(fit2, newdata = finaltime_data), na.rm = T)

# Simulate 1000 observations considering the uncertainty
# and look at the distribution.
set.seed(421)

hist(rnorm(1000, mean_cd4, sd = sd_cd4))
```

```{r}
cd4 <- subset(cd4, !is.na(VDATE))
cd4[cd4$VDATE == max(cd4$VDATE, na.rm = T), ]
mean(c(39.0, 21.2))
```

So our predictions are extremely uncertain. Over half our simulations are underestimating the date and a handful are overestimating the results. It looks like our model is terrible at predicting that final time point


SECOND VERSION:

```{r}
#create data 
final.time.data <- subset(cd4, !is.na(treatmnt) & !is.na(baseage))
final.time.data <- final.time.data[complete.cases(final.time.data), ]
#force time to be last date "final" (and remove omissions)
final.time.data$VDATE <- max(as.Date(final.time.data$VDATE,format="%m-%d-%Y"), na.rm = T)

#calculate mean and sd from new data
cd4.mean <- mean(posterior_predict(fit2, newdata = final.time.data), na.rm = T) #mean 
cd4.sd <- sd(posterior_predict(fit2, newdata = final.time.data), na.rm = T) #standard deviation

#simulate 1000 times 
set.seed(100)
hist(rnorm(1000, cd4.mean, cd4.sd))

#Compare distribution at final time point for actual data 
hist(final.time.data$CD4PCT.sqrt)
```


THIRD VERSION, only works with LMER, not with STAN_GLMER:

```{r setup, include=FALSE}
library(lme4)
d <- cd4

#y.tilde<- #wanted
fit3 <- lmer(sqrtCD4 ~ time + treatmnt + baseage + (1 | newpid), data=d)

#generate dataset to store results
new.d<-data.frame(y.tilde=rep(NA,nrow(d)),d$visage,d$baseage)

#simulate data for final time point
final.time<-max(d$time)
#final.time<-max(d$VDATE)
which.id<-d[which(d$time==final.time),"newpid"]
treatmnt<-d$treatmnt
baseage<-d$baseage

a.hat.M2 <- fixef(fit3)[1] + fixef(fit3)[3]*treatmnt + fixef(fit3)[3]*baseage + ranef(fit3)$newpid
b.hat.M2 <- fixef(fit3)[2]

set.seed(123)
x.tilde <- final.time
sigma.y.hat <- sigma.hat(fit3)$sigma$data
coef.hat <- as.matrix (coef(fit3)$newpid)[which.id,]
y.tilde <- rnorm (nrow(d), coef.hat %*% c(1, x.tilde, d$treatmnt[which.id],d$baseage[which.id]), sigma.y.hat)
mean(y.tilde) #3.865065


## repeat and compare posterior distribution
n.sims <- 1000
sims.array<-array(NA,dim=c(nrow(d),n.sims))
for(i in 1:n.sims){
print(i)
    sims.array[,i]<-rnorm (nrow(d), coef.hat %*% c(1, x.tilde, d$treatmnt[which.id],d$baseage[which.id]), sigma.y.hat)
}
```

```{r}
hist(colMeans(sims.array),30,xlim=c(3.7,4.3),col="black")
abline(v=d[which.id,"sqrt"],col="red")
```




And $\textbf{3.5$
```{r}

```

