---
title: "hw23"
author: "Tin, Jade"
date: "4/173/2018"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


$\textbf{2.3}$

$\textbf{(a)}$

Using the following code in data wrangler, this was simpler to obtain:



extract col: column1 at: 15,22
extract col: column1 at: 24,31
extract col: column1 at: 33,40
extract col: column1 at: 42,50
extract col: column1 at: 51,58
extract col: column1 at: 60,67
extract col: column1 after: `  ` before: `{end}`
extract col: column1 on: `7 |6 |5 |4 |3 |2 |  |1 |pair`
extract col: column1 on: `Performance|Program|criterion `
keep row: in(sourcerownumber(), [21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32, 33, 34, 35])
drop col: column1
replace col: column9 with: '' on: `  ` global: true
set col: column9 value: fill(ifmissing($col, null())) order: sourcerownumber()




Loading the exported result olympics1932_a.csv into R, we can see that the data is in the desired format:


```{r}
oly_a <- read.csv("~/Desktop/olympics1932_a.csv")
oly_a
```


$\textbf{(b)}$

Again, using the data wrangler with the following code yeilds the olyb2 and olyb1 csvs which we then simply merge in R and  effectively append the reulst to itself to get the desired output. Wrangler queries:


to get the olyb1 which contains all variables bar "program", and olyb2, which contains all but "performance", for the pairs


extract col: column1 at: 15,22
extract col: column1 at: 24,31
extract col: column1 at: 33,40
extract col: column1 at: 42,50
extract col: column1 at: 51,58
extract col: column1 at: 60,67
extract col: column1 after: `  ` before: `{end}`
extract col: column1 on: `7 |6 |5 |4 |3 |2 |  |1 |pair`
extract col: column1 on: `Performance|Program|criterion `
keep row: in(sourcerownumber(), [21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32, 33, 34, 35])
drop col: column1
replace col: column9 with: '' on: `  ` global: true
set col: column9 value: fill(ifmissing($col, null())) order: sourcerownumber()
header
valuestocols col: criterion value: 1 default: 0
unpivot col: judge_7, judge_6, judge_5, judge_4, judge_3, judge_2, judge_1
drop col: criterion
unpivot col: value1
drop col: key2
derive value: Program * value2 as: 'prog'
derive value: Performance * value2 as: 'perf'
drop col: Performance,Program
drop col: value2
delete row: matches([perf], `0`)
drop col: prog


second chunk, for olyb2 file, effecyively the same but:
... 
delete row: matches([prog], `0`)
drop col: perf



These are simply combined in R to obtain the output, but for the pairs. To get it for the skaters, we effectively append the reusult to itself to get the desired output. 
```{r}
olyb2 <- read.csv("~/Desktop/olympics1932b2.csv")
olyb1 <- read.csv("~/Desktop/olympics1932b1.csv")

olyb2$performance <- olyb1$perf
colnames(olyb2)[colnames(olyb2)=="prog"] <- "program"


olyb3 <- olyb2
colnames(olyb3)[colnames(olyb3)=="pair"] <- "skaterID"
olyb3$skaterID <- olyb3$skaterID + 7
colnames(olyb2)[colnames(olyb2)=="pair"] <- "skaterID"
colnames(olyb2)[colnames(olyb2)=="key1"] <- "judgeID"
colnames(olyb3)[colnames(olyb3)=="key1"] <- "judgeID"
olyb3 <- olyb3[,c(4,3,1,2)]
olyb2 <- olyb2[,c(4,3,1,2)]
oly_b <- rbind(olyb2, olyb3)

write.csv(oly_b, "oly_b.csv", row.names=F)   
oly_b
```



$\textbf{(c)}$

