---
title: "hw25"
author: "Tin, Jade"
date: "4/29/2018"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
#install.packages("rstanarm")
```

$\textbf{3.2}$


```{r include=FALSE}
library(rstanarm)
library(ggplot2)
library(arm)
library(dplyr)
#install.packages("R2WinBUGS")
#install.packages("rstanarm")
```



```{r}
cd4 <- read.csv("http://www.stat.columbia.edu/~gelman/arm/examples/cd4/allvar.csv")
# cd4 <- read.csv("~/Desktop/allvar.csv")
cd4$sqrtCD4 <- sqrt(cd4$CD4PCT)       
cd4$time <- cd4$visage - cd4$baseage
cd4<- cd4[-which(is.na(cd4$time)),]
cd4<- cd4[-which(is.na(cd4$CD4PCT)),]
```


We need the previous exercise to complete $\textbf{(3.4)}$


$\textbf{3.3 (a)}$

```{r include=FALSE}
fit2 <- stan_glmer(sqrtCD4 ~ time + treatmnt + baseage + (1 | newpid),  data = cd4)
```
Use the model fit from Exercise 3.2(b) to generate simulation of predicted CD4 percentages for each child in the dataset at a hypothetical time point. 
```{r}
#Removing all rows with NAs because posterior_predict doesn't allow for NAs
pred_data_= cd4[complete.cases(cd4), ]

#Selecting a hypothetical time point
pred_data_$VDATE <- as.Date("1999-04-29")
#Estimating the predicted CD4 percentage for each child
newpred <- posterior_predict(fit2, newdata = pred_data_)

```

$\textbf{3.3 (b)}$
Use the same model fit to generate simulations of CD4 percentages at each of the time periods for a new child who was 4 years old at baseline. 

```{r}
#subsetting original cd4 for only when baseage is close to 4 (there is no observation where age is exactly 4)
pred_data_4yr <- subset(cd4, (baseage  > 3.99 & baseage < 4.01)) 

#removing NAs
pred_data_4yr= pred_data_4yr[complete.cases(pred_data_4yr), ]

#indicating new child with new newpid
pred_data_4yr$newpid = 300

#feed into model
pred_4yr <- posterior_predict(fit2, newdata = pred_data_4yr)


```


On to exercise $\textbf{3.4}$


```{r}
final_data <- cd4[complete.cases(cd4), ]
final_data$VDATE <- max(as.Date(final_data$VDATE,format="%m/%d/%Y"), na.rm = T)


fin_actual <- cd4[complete.cases(cd4), ]
fin_actual$VDATE <- max(as.Date(fin_actual$VDATE,format="%m/%d/%Y"), na.rm = T)

mean.cd4 <- mean(posterior_predict(fit2, newdata = final_data), na.rm = T)
sd.cd4 <- sd(posterior_predict(fit2, newdata = final_data), na.rm = T)

set.seed(10)

hist_sim <- as.data.frame(rnorm(1000, mean.cd4, sd = sd.cd4))
hist_sim$x <- hist_sim$`rnorm(1000, mean.cd4, sd = sd.cd4)`
hist(rnorm(1000, mean.cd4, sd = sd.cd4))

  
ggplot() + geom_histogram(data=hist_sim, aes(hist_sim$x), col="blue", fill="green") + theme_light() + labs(x="simualuted") 

ggplot() + geom_histogram(data=fin_actual, aes(fin_actual$sqrtCD4), col="white", fill="grey") + theme_light() + labs(x="actual") 
```


$\textit{Shadow topic: a neater way to compare}$

```{r}
ggplot() + geom_density(data=hist_sim, aes(hist_sim$x), col="blue", fill="green", alpha = 0.3) + theme_light() + labs(x="simualuted") + geom_density(data=fin_actual, aes(fin_actual$sqrtCD4), col="blue", fill="grey", alpha = 0.3) + labs(title = "green - simulated; grey - actual", y ="Density") 
```



And $\textbf{3.5}$
```{r include=FALSE}
#install.packages("mosaic")
library('mosaic')
library('rstanarm')

# 3.  Multilevel model including uranium as a county-level predictor
srrs2 = read.table('http://www.stat.columbia.edu/~gelman/arm/examples/radon/srrs2.dat', 
                   header=T, sep=",")


# read in and clean the data
mn <- srrs2$state=="MN"
radon <- srrs2$activity[mn]
log.radon <- log (ifelse (radon==0, .1, radon))
floor <- srrs2$floor[mn]       # 0 for basement, 1 for first floor
n <- length(radon)
y <- log.radon
x <- floor

# get county index variable

county.name <- as.vector(srrs2$county[mn])
uniq <- unique(county.name)
J <- length(uniq)
county <- rep (NA, J)
for (i in 1:J){
  county[county.name==uniq[i]] <- i
}

# get the county-level predictor

sample.size <- as.vector (table (county))
sampleSize.full = sample.size[county]

```

```{r include=FALSE}
# fit the model using stan_glmer
options(mc.cores = parallel::detectCores())
M1 <- stan_glmer(y ~ x + sampleSize.full + (1 | county))
```

```{r}
print (M1)
```






