---
title: "hw22"
author: "Tin, Jade"
date: "4/13/2018"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


\textbf{2.1}

\textbf{(a)}

Write the notation for a varying-intercept multilevel logistic regression (with community districts as the groups for the probability of rodent infestation using the individual-level predictors but no group-level predictors.
```{r}
rodents = read.table("http://www.stat.columbia.edu/~gelman/arm/examples/rodents/apt.dat")
colnames(rodents)
```
The Rodent dataset contains y (the probability of getting a rodent infestation), and other characteristics of the unit, defects, poor, race, floor, dist and bldg. Although race, floor, dist, bldg are categorical variables that can be treated as group-levels, for the purpose of this exercise, we will run a multi-level logistic regression with community district (var dist) as groups, and maintain all the other categorical variables as predictors for simplicity. 
With this assumption, we will have following model notation: 
$n$ is the number of observations (units) in the Rodent dataset. 

$$ \Pr (y_j = 1) = \text{logit}^{-1} \left(\beta_{0} + \beta_{1}\text{poor} + \beta_{2} \text{race} + \beta_{3} \text{floor} + \beta_{4} \text{building} + \beta_{5} \text{defects} +  \alpha_{j[i]} \right)$$ 


for $1, \dots, n$, where $n = 15894$


\textbf{(b)}

Expand the model in (a) by including the variables in dist.dat as group level predictors 
We have 55 districts in the Rodent dataset, therefore j goes from 1 to 55. The following handwritten equation represents the second step of the multi-level regression that takes into account group level predictors. These predictors, as shown below, are dist.defects and dist.poor. 
```{r}
dist_info = read.table("http://www.stat.columbia.edu/~gelman/arm/examples/rodents/dist.dat")
colnames(dist_info)
```


$$ \alpha_{j} \sim N \left( U_{j} \gamma , \quad \sigma_{2 \alpha} \right) $$

for $j = 1, dots, 55$

$U$ is the amtrix of ddistrict level predictors, dist.defects and dist.poor. $\gamma$ is the vector of coefficients for the district-level regression, andd $\sigma_\alpha$ is the standard edviation of the unexplained group-level errors




```{r}
library("arm")
library("rstanarm")
require(foreign)
allvar <- read.csv("~/Desktop/allvar.csv")
head(allvar)
```

$\textbf{2.4:}$

$\textbf{(a)}$
```{r}

allvar$time <- allvar$visage - allvar$baseage
allvar$sqrt_cd4 <- sqrt(allvar$CD4PCT)
allvar<- allvar[-which(is.na(allvar$time)),]
allvar<- allvar[-which(is.na(allvar$CD4PCT)),]
head(allvar)
```


```{r fig.height=10, fig.width=13}
library(ggplot2)
ggplot((allvar), aes(x=time, y=sqrt_cd4)) + xlab("Time") + ylab("sqrt(CD4 Percentage)") +
  geom_line(aes(col=as.factor(newpid), alpha=0.3)) + theme(legend.position="none") + theme_light() + theme(legend.position="none")
```


$\textbf{(b)}$

```{r fig.height=10, fig.width=13}
library(ggplot2)
ggplot(allvar, aes(x=time, y=sqrt_cd4) ) + 
        geom_point(aes(color = factor(allvar$newpid))) +
        geom_line(stat = "smooth", method = lm, aes(color = factor(allvar$newpid)), se = FALSE, alpha = 0.3) +
        scale_color_discrete(name="id") + 
        theme_light() + theme(legend.position="none")
```



$\textbf{(c)}$

```{r}
fit1 <- lmer(sqrt_cd4 ~ time + (1 + time | newpid), data=allvar)
display(fit1)
```

```{r}
cofs <- coef(fit1)
cofss <- do.call("rbind", as.list(cofs))

uniq <-by(allvar, allvar$newpid, tail, n=1)
uniq_c<-do.call("rbind", as.list(uniq))

```

```{r}
uniq_c$intercept <- cofss$"(Intercept)"
uniq_c$slope <- cofss$"time"
cbind(uniq_c, cofss)
```

```{r}
fit2 <- lm(intercept ~ treatmnt + baseage, data=uniq_c)
display(fit2)

fit3 <- lm(slope ~ treatmnt + baseage, data=uniq_c)
display(fit3)
```


$\textit{Shadow topic:}$

To estimate the 
Using lmer with time + (1 + time | child) to have the slopes and the intercepts vary by child, and adding all of treatment, baseage, time:baseage, time:treatment, as additional group(child)-level predictors, with the interactions allowing treatment and baseage to be predictors in the regressions for the slopes as well as for the intercepts:


```{r}
fit5 <- lmer(sqrt_cd4 ~ time + treatmnt + baseage + time:baseage + time:treatmnt + (1 + time | newpid), data=allvar)
display(fit5)
```


