---
title: "Partial Regression Plots"
author: "Tin"
date: "4/12/2018"
output:
  pdf_document: default
  html_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(arm)
df <- read.csv("~/Desktop/soccer_prominence.csv")
```



Looking at the ddirect relationship between $\textbf{log_media_mentions}$ and $\textbf{log_transfer_value}$:

```{r fig.height=4, fig.width=6}
library(ggplot2)
df$log_transfer_value <- log(df$transfer_value)
df$log_media_mentions <- df$logmentions
df$FIFA_quality <- df$primary
df$age_at_transfer <- df$transfer_age
# look at direct relationship for "mentions"
ggplot(df, aes(x=logmentions, y=log_transfer_value)) + geom_point() + theme_light() + ylab("log(transfer value)") + xlab("log(media mentions)") + geom_smooth(method='lm', se=FALSE)
```



Run the linear model:
```{r}
simple_model <- lm(log_transfer_value ~ log_media_mentions + FIFA_quality + age_at_transfer, data = df)
```

```{r}
summary(simple_model)
```
```{r}
display(simple_model)
```

For a given regression model:

$$ Y_i = \alpha + \beta X_i_1 + \gamma X_i_2 + \delta X_i_3 + \epsilon_i^1 $$



Partial regression plots are obtained by computing:

$\textbf{(i)}$ the residuals regressing the dependent variable against the independent variables but omitting the independent variable of interest:


$\textbf{(ii)}$ the residuals from regressing the independent variable of interest against the remaining independent variables, and $\textbf{(iii)}$ plotting the residuals from step (i) against the residuals from (ii). 

The benefit of this plot is that the least squares linear fit has the slope $\beta_{i}$ (of the variable of interest in the original model) and intercept zero.


```{r}
#install.packages("car")
library("car")
```

The partial regression plot (Added Variable Plot), for the variable of interest $log$ from the multiple regression model.

```{r fig.height=6, fig.width=6}

avPlots(simple_model, "log_media_mentions", col = "Black", col.lines = "Blue", lwd= 3, 
       ylab = "residuals from regressing y on everything but x1:   log(transfer values) ~ EVERYTHING BUT log(media mentions)",
       xlab ="residuals from regressing x1 on all the other predictors:  log(media mentions) ~ remainings predictors", grid = FALSE,
       main = "Partial Regression Plot: Media Mentions")
```
```{r fig.height=8, fig.width=6}
avPlots(simple_model, col = "Black", col.lines = "Blue", lwd= 3)
```


