---
title: "hw20"
author: "Jade, Tin"
date: "4/3/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\textbf{18.6 (a)}
Variables recorded pre-treatment: lactation number, age, initial weight of cow
4 diets (treatment): different levels of addictive

```{r}
library("arm")
require(foreign)
options(mc.cores = parallel::detectCores())
cows <- read.table("http://www.stat.columbia.edu/~gelman/arm/examples/cows/cow.dat", header=TRUE, skip=3)
colnames(cows)
fit = glm(fat ~ level, data = cows)
display(fit)

```

Why is this not a completely appropriate analysis given the randomization used?

Usually, when assumptions about the relevant covariates' being balanced across (multiple) treatment groups are satisfied, one may even rely on a model like the one above; however, the randomization, whose details remain murky (as the problem puts it, it's not clear when the decision to rerandomize was made or wasn't), was less than ideal and effectively corresponded to redoing it until a desired assignment was observed, which strictly speaking is not random. In this context, instead of tampering with the randomization, it would have been more appropriate to include the relevant covariates in the regression model, in order to address the possible imbalance in the relevant covariates of the original random assignment of the various treatments.

Among other issues not necessarily related to the manner in which the treatment assignment was rerandomized several times, another possible problem with the model is a potential the violation of the Stable Unit Treatment Value Assumption (SUTVA) assumption. The SUTVA assumption requires that the response of a particular unit depends only on the treatment to which it was assigned, not the treatments of other units around it. The effectively almost hand-picked selection of treatment groups ensures that cows in each group have similar distributions of the relevant covariates. However, as is known to be the case in agricultural environments, interferences between units are usually expected. For example, one group of cow receiving one level of treatment may be prone to a certain mood change, which induce them to produce less milk. This mood change may spillover from one area to another (the way that the treatment doesn???t), affecting other cows to also produce less milk, regardless of their treatment level.

\textbf{Shadow topic:}


```{r}

```

